Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-12-22 paper/paper.tex
Implement changes 20181212

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\DeclareCaptionLabelSeparator{bar}{  \textbar\quad}
\usepackage[labelsep=bar, labelfont=bf]{caption}
\newcommand{\Fig}{Fig.}
% \usepackage{lineno}
% \linenumbers

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}

\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes \cite{Karnik_2007}, field-effect
transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to their ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as the
desalination membrane enables excellent salt rejection by preventing
the permeation of hydrated ions with a high water permeability
simultaneous
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
the fabrication of subnanometer porous 2D membranes over a large area
with atomic precision remains technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores can significantly diminish salt
rejection.  Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial that if the surface charges can result in a degree of
salt rejection, as the membrane charge and potential cannot be
precisely quantified and are sensitive to the surroundings and
chemical treatment \cite{Li_2008}. The difficulty in turn hinders a
fundamental understanding of the interactions between the atomically
thin 2D membrane and the electrolyte solution. Here, we demonstrate
macroscopic salt rejection through a sheet of large-area porous
graphene using electrostatic gating, thereby deepening the
understanding of ion-graphene interaction and its implications on
nanoporous graphene-based desalination applications.

@@

where $x$ is the molar fraction in solution, $z$ is the ionic valence,

@@

$\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to the

@@

where $\Delta \phi_{\mathrm{G}}$ is the change of graphene’s work
function. Under the assumption that the charge neutrality point of
graphene coincides with the Dirac point at $V_{\mathrm{G}}$ = 0, the elementary

@@

velocity of graphene (more details find Supplementary Section
S5). Note that the PG film fabricated experimentally is double-layer
turbostratic graphene, in which we assume the

@@

self-consistently by discretizing Eqs. \eqref{eq:pnp}-\eqref{eq:poisson}
using the finite-element method (FEM), in which the graphene surface
potential is coupled with

@@

graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene synthesized
by chemical vapor deposition (CVD) used in our experiments, it is
well-recognized that the electron traps are inherently introduced
during synthesis and patterning \cite{Dean_2010}, effectively reducing
the charge density and surface potential on graphene
$V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3). With the nonideality in
mind, hereafter, we compare the calculations and experiments in the
regime of $V_{\mathrm{G}}>0$. For example, \Fig{} \ref{fig:3}c
presents the calculated $\sigma_{\mathrm{G}}$ and $\psi_{\mathrm{G}}$
as a function of $V_{\mathrm{G}}$ considering the ionic diffusion
through a single 20 nm-diameter nanopore drilled on a sheet of
semi-infinite double layer graphene that separates HCR containing KCl
solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in axisymmetric
coordinates (details see Supplementary Section S5). Indeed, the
interplay between graphene quantum capacitance and the EDL
significantly reduces the graphene surface potential

@@

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary \Fig{} S4). We also
observe that $\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary \Fig{}
S5). The observations confirm the distinct ionic
transport pathways upon applying a positive $V_{\mathrm{G}}$: pore
center for cations and pore edge for anions. \Fig{} \ref{fig:4}c
presents the calculated \textit{z}-component of the cation and anion fluxes
through the pore at the graphene plane (z = 0), $\boldsymbol{J}_{z}$
,as a function of the normalized radius, $r/R_{\mathrm{G}}$ , where
$r$ is the radial coordinate and $R_{\mathrm{G}}$ is the pore radius,
at different $V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$
is negative because the LCR is placed at z$<$0 in the simulation box. At
$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6). Intriguingly,
by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
over diffusion flux and (ii) the concentration near the pore edge
(prefered path) greatly increases (details see Supplementary Section
S6, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
cannot be reached experimentally in graphene membrane, as this
requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
electrochemical reactions \cite{Toh_2011}. On the other hand, in an
IFET, the electric potential on the pore wall is considerably higher,
equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
electrode (having an infinitely-large quantum capacitance). We
therefore conclude that the quantum capacitance-induced nonlinear
damping in the surface potential results in the observed salt
rejection.  Following the above discussions, we further investigate
the physical limits for the biased graphene nanopores. Specifically,
the salt rejection characteristics are controlled by: (i) the overlap
of EDL inside the nanopore, essentially controlled by two length
scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
graphene surface potential $\psi_{\mathrm{G}}$ controlled by
$V_{\mathrm{G}}$ following Eq. \eqref{eq:Vg}. To this end, we
calculate $\psi_{\mathrm{G}}$ as a function of
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
a higher $V_{\mathrm{G}}$ is required to reach the same level of
$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
the calculated salt rejection factor $\xi$ increases with both
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
with the experimentally observed $\xi - c_{0}$ dependence. We also
find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.

@@

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary
Section S7). Similar to the KCl system discussed earlier, the salt
rejection is more pronounced in the positive $V_{\mathrm{G}}$
regime. The degree of salt rejection deceases with the salt valance;
for example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our simulations,
in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
the same simulation setups(\Fig{} \ref{fig:6}b). The calculated
$\xi_{\mathrm{max}}$ values are quantitatively compared with
experiments (\Fig{} \ref{fig:6}c), and the same trend is
observed. Indeed, because the Debye length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). We notice that without
any fitting parameters, our theory can predict the experimental values
reasonably well. In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of salt diffusivity is
negligible. This finding also explains the concentration dependence of
$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.

>>>>

\documentclass[journal=langd5,email=true, hyperref=true, keywords=false]{achemso}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{times}
\usepackage{todonotes}
\DeclareCaptionLabelSeparator{bar}{  \textbar\quad}
\usepackage[labelsep=bar, labelfont=bf]{caption}
\newcommand{\Fig}{Fig.}
\usepackage{lineno}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}
\linenumbers
\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
manipulate transport phenomena at nanometer scale to enable new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes \cite{Karnik_2007}, field-effect
transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}, Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to their ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as the
desalination membrane enables excellent salt rejection by preventing
the permeation of hydrated ions with a high water permeability
simultaneous
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
the fabrication of subnanometer porous 2D membranes over a large area
with atomic precision remains technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores can significantly diminish salt
rejection.  Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial that if the surface charges can result in a degree of
salt rejection, as the membrane charge and potential cannot be
precisely quantified and are sensitive to the surroundings and
chemical treatment \cite{Li_2008}. The difficulty in turn hinders a
fundamental understanding of the interactions between the atomically
thin 2D membrane and the electrolyte solution. Here, we demonstrate
macroscopic salt rejection through a sheet of large-area porous
graphene using electrostatic gating, thereby deepening the
understanding of ion-graphene interaction and its implications on
nanoporous graphene-based desalination applications.

@@

 $x$ is the molar fraction in solution, $z$ is the ionic valence,

@@

$\psi_{\mathrm{G}}$, is not equivalent to $V_{\mathrm{G}}$ due to
change of graphene's work function upon charging, known as the

@@

where
$\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
\phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
function. The properties of the PG samples fabricated is close to
intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
to be XXX $e \cdot$cm$^{-2}$, corresponding to a work function
difference of XXX meV from graphene's Dirac point (details see
Supplementary Section SXX), much smaller than the
$\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
simplification that the charge neutrality point of graphene coincides
with the Dirac point at $V_{\mathrm{G}}$ = 0. The elementary

@@

velocity of graphene (more details find Supplementary Section S5).
Note that the PG film fabricated experimentally is double-layer
turbostratic (randomly aligned) graphene, in which we assume the

@@

self-consistently by discretizing
Eqs. \eqref{eq:pnp}-\eqref{eq:poisson} using the finite-element method
(FEM), in which the graphene surface potential is coupled with

@@

graphene (Eq. \eqref{eq:delta-phiG}). However, for graphene
synthesized by chemical vapor deposition (CVD) used in our
experiments, it is well-recognized that the electron traps are
inherently introduced during synthesis and patterning
\cite{Dean_2010}, effectively reducing the charge density and surface
potential on graphene $V_{\mathrm{G}}<0$ (Supplementary \Fig{} S3),
which is related to the fact that observed $\xi$ is much lower within
the $V_{\mathrm{G}}<0$ regime in \Fig{} \ref{fig:2}c. With the
nonideality in mind, hereafter, we compare the calculations and
experiments in the regime of $V_{\mathrm{G}}>0$. For example, \Fig{}
\ref{fig:3}c presents the calculated $\sigma_{\mathrm{G}}$ and
$\psi_{\mathrm{G}}$ as a function of $V_{\mathrm{G}}$ considering the
ionic diffusion through a single 20 nm-diameter nanopore drilled on a
sheet of semi-infinite double layer graphene that separates HCR
containing KCl solution at $c_{0}$ = 0.1 mM, and LCR at $c_{0}/10$ in
axisymmetric coordinates (details see Supplementary Section
S5). Indeed, the interplay between graphene quantum capacitance and
the EDL significantly reduces the graphene surface potential

@@

We further reveal the cation and anion transport pathways by looking
into their electrochemical potentials (\Fig{} \ref{fig:4}b). By
increasing $V_{\mathrm{G}}$, a more positive $\psi_{\mathrm{G}}$ on
graphene surface reduces the cation concentration at the pore edge due
to the electrostatic interactions, thereby increasing its
concentration gradient at the pore center. On the other hand, the
anion concentration near the pore edge increases exponentially, such
that the concentration gradient at the pore center becomes
small. (also see Supplementary \Fig{} S4). We also observe that
$\Delta \mu_{+}$ is dominated by the concentration, while
$\Delta \mu_{-}$ is much less than $\Delta \mu_{+}$ due to the balance
between the diffusion and drift potentials (see Supplementary \Fig{}
S5). The observations confirm the distinct ionic transport pathways
upon applying a positive $V_{\mathrm{G}}$: pore center for cations and
pore edge for anions. \Fig{} \ref{fig:4}c presents the calculated
\textit{z}-component of the cation and anion fluxes through the pore
at the graphene plane (z = 0), $\boldsymbol{J}_{z}$ ,as a function of
the normalized radius, $r/R_{\mathrm{G}}$ , where $r$ is the radial
coordinate and $R_{\mathrm{G}}$ is the pore radius, at different
$V_{\mathrm{G}}$ values. Note that $\boldsymbol{J}_{z}$ is negative
because the LCR is placed at z$<$0 in the simulation box. At
$V_{\mathrm{G}}$ = 0 (pure diffusion), the anion and cation flux
profiles are identical, with a higher flux near the pore edge, which
is expected, as the concentration gradient is higher. By gradually
increasing $V_{\mathrm{G}}$, both fluxes are reduced throughout the
pore, while the degree of reduction is more pronounced at the pore
edge for the cation, and at the pore center for the anion, following
the scenarios we discussed above. Accordingly, the integrated fluxes
across the pore, $|\boldsymbol{J}_{z}|$, are reduced with
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:4}d). A total flux reduction of up
to 80\% is predicted. Another interesting finding here is that, by
increasing $V_{\mathrm{G}}$, the nanopore transport preferentially
allows cations over anions, or in other words, the anion flux is more
reduced with $V_{\mathrm{G}}$ (see \Fig{} \ref{fig:4}c), known as the
ion selectivity of graphene nanopore \cite{Rollings_2016}. In our setup, the imbalance between cation and anion
fluxes near the graphene nanopore is compensated by the EDL formation
at the counter-electrode in LCR, which maintains the electroneutrality
of the system. Notably, since atomically thin graphene samples are
used, the mechanism of salt rejection is clearly distinct from that in
capacitive deionization \cite{Li_2010}, where electrodes with large
surface area are required.

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6). Intriguingly,
by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
over diffusion flux and (ii) the concentration near the pore edge
(prefered path) greatly increases (details see Supplementary Section
S6, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
cannot be reached experimentally in graphene membrane, as this
requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
electrochemical reactions \cite{Toh_2011}. On the other hand, in an
IFET, the electric potential on the pore wall is considerably higher,
equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
electrode (having an infinitely-large quantum capacitance). We
therefore conclude that the quantum capacitance-induced nonlinear
damping in the surface potential results in the observed salt
rejection.  Following the above discussions, we further investigate
the physical limits for the biased graphene nanopores. Specifically,
the salt rejection characteristics are controlled by: (i) the overlap
of EDL inside the nanopore, essentially controlled by two length
scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
graphene surface potential $\psi_{\mathrm{G}}$ controlled by
$V_{\mathrm{G}}$ following Eq. \eqref{eq:Vg}. To this end, we
calculate $\psi_{\mathrm{G}}$ as a function of
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
a higher $V_{\mathrm{G}}$ is required to reach the same level of
$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
the calculated salt rejection factor $\xi$ increases with both
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
with the experimentally observed $\xi - c_{0}$ dependence. We also
find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
\todo[inline]{Some comments for large $\xi$ values after considering
  the transport resistance can be shown here.}

@@

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary Section
S7). Similar to the KCl system discussed earlier, the salt rejection
is more pronounced in the positive $V_{\mathrm{G}}$ regime. The degree
of salt rejection deceases with the salt valance; for example, the
measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V decreases from $>$
0.5 for monovalent NaCl to -0.04 for multivalent
K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our
simulations, in which we calculate $\xi$ as a function of
$V_{\mathrm{g}}$ using the same simulation setups(\Fig{}
\ref{fig:6}b). The calculated $\xi_{\mathrm{max}}$ values are
quantitatively compared with experiments (\Fig{} \ref{fig:6}c), and
the same trend is observed. Indeed, because the Debye length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). Similar to the
experimenal observations, small difference between the $\xi$ of salts
with same valence (e.g. LiCl, NaCl and KCl) is also predicted from the
simulations due to the variation in ionic mobilities. We notice that
without any fitting parameters, our theory can predict the
experimental values reasonably well.  In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of Debye length is dominant over
the salt diffusivity. This finding also explains the concentration
dependence of $\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$. Further including the
specific interaction of ionic species with the graphene membrane
\cite{Ghosh_2018} may give even better agreement with experimental
results.
